\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.4in,top=0.3in,right=0.4in,bottom=0.3in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Jaman Uddin} % Your name
\address{\textbf{Software Engineer}}    % Role you are applying for
\address{+880 167 385-0025 \\ Uttara, Dhaka, Bangladesh}
\address{\href{mailto:swe.jaman.me@gmail.com}{swe.jaman.me@gmail.com} \\ \href{https://github.com/RootProgrammer}{github.com/RootProgrammer}}

% \address{\href{mailto:swe.jaman.me@gmail.com}{swe.jaman.me@gmail.com} \\ \href{https://www.linkedin.com/in/swe-jaman-me/}{linkedin.com/in/swe-jaman-me} \\ \href{https://github.com/RootProgrammer}{github.com/RootProgrammer}}

\begin{document}

%----------------------------------------------------------------------------------------
%	PROFESSIONAL SUMMARY
%----------------------------------------------------------------------------------------

\begin{rSection}{PROFESSIONAL SUMMARY}

{Proactive and results-driven Software Engineer with \textbf{2+ years of experience} in \textbf{Python} and \textbf{Django} development. Specializing in \textbf{architecting scalable software solutions} and leading high-performing teams in fast-paced environments. Demonstrated success in reducing operational costs, enhancing system efficiency, and streamlining deployment processes. Strong expertise in \textbf{Agile methodologies} and \textbf{cross-functional collaboration}, ensuring project goals are achieved on time and within budget. Passionate about adopting cutting-edge technologies like \textbf{AI/ML} and driving continuous learning to foster team growth and innovation.}

\end{rSection}

%----------------------------------------------------------------------------------------
% SKILLS
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\renewcommand{\arraystretch}{1.5}
\begin{tabular}{@{} >{\bfseries}l @{\hspace{6ex}} >{\raggedright\arraybackslash}p{14.2613cm}}
Technical Leadership & Mentoring, Code Reviews, Architecture Design, Best Practices\\

Programming Languages & Python, Django, JavaScript, React.js, TypeScript, Node.js, Go, Flutter\\

Frameworks & Django REST Framework, FastAPI\\

DevOps & Docker, Terraform, CircleCI\\

Cloud Technologies & Google Cloud Platform, RDBMS (Postgres, MySQL), NoSQL (MongoDB)\\

Project Management & Agile, Cross-Functional Team Collaboration, Problem Solving, Innovation\\

Development Tools & Git, GitHub, Jupyter, VS Code, JetBrains, JIRA, Confluence\\
\end{tabular}\\
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{WORK EXPERIENCE}

\textbf{Software Engineer} \hfill Jan 2022 - Apr 2024\\
imranslab \hfill \textit{Montréal, QC (Remote)}

\textbf{Technical Leadership:}
 \begin{itemize}
    \item Spearheaded Python/Django projects, mentoring a cross-functional team to ensure scalable, high-performance software.
    \item Conducted regular code reviews ensuring best practices, design principles, and coding standards were met.
 \end{itemize}

\textbf{Development \& Architecture:}
 \begin{itemize}
    \item Led the design and development of scalable Python applications, enhancing system efficiency by 40\%.
    \item Migrated legacy systems to cloud-based infrastructure, reducing operational costs by 20\% and deployment cycles by 30\%.
 \end{itemize}

\textbf{Project Management:}
 \begin{itemize}
    \item Worked closely with project managers, providing technical insights and ensuring timely delivery of project milestones.
    \item Collaborated with diverse teams to define and translate business requirements into technical solutions.
 \end{itemize}

\textbf{Innovation \& Continuous Learning:}
 \begin{itemize}
    \item Advocated for the adoption of emerging Python technologies and frameworks, staying ahead of industry trends.
 \end{itemize}

\textbf{SWE Intern} \hfill Jun 2021 - Dec 2021\\
imranslab \hfill \textit{Montréal, QC (Remote)}

\begin{itemize}
    \item Refactored 5000 lines of legacy code into a modular, maintainable structure, improving code maintainability by 50\%.
    \item Led a project to migrate local servers to the cloud, increasing scalability and reducing server downtime by 35\%.
\end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}

\begin{itemize}
    \item \textbf{AI-Enhanced Job Finder:} Developed a job finder platform using Django and React, integrating AI algorithms to refine resume evaluations, boosting match accuracy by 25\%.
    \item \textbf{Inventory Management System:} Designed and implemented a scalable inventory system using Django, improving data accuracy by 50\% and reducing inventory costs by 15\%.
\end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{EDUCATION}

{\bf B.Sc.(Engg.) in Computer Science and Engineering (CSE)}, Asian University of Bangladesh \hfill {2018 - 2022}

\end{rSection}

\end{document}
