\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.4in,top=0.3in,right=0.4in,bottom=0.3in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Jaman Uddin} % Your name
\address{\textbf{Full Stack Developer}}    % Role you are applying for
\address{+880 167 385-0025 \\ Uttara, Dhaka, Bangladesh}
\address{\href{mailto:zamaan.md19@gmail.com}{zamaan.md19@gmail.com} \\ \href{https://www.linkedin.com/in/rootprogrammer/}{linkedin.com/in/rootprogrammer} \\ \href{https://github.com/RootProgrammer}{github.com/RootProgrammer}}

\begin{document}

%----------------------------------------------------------------------------------------
%	PROFESSIONAL SUMMARY
%----------------------------------------------------------------------------------------

\begin{rSection}{PROFESSIONAL SUMMARY}

{Full Stack Developer with two years of experience specializing in Django (back-end) and React (front-end). Proven track record in developing and maintaining web applications, enhancing performance, and collaborating with cross-functional teams. Skilled in Agile methodologies, committed to delivering high-quality, responsive applications.}

\end{rSection}

%----------------------------------------------------------------------------------------
% SKILLS
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\renewcommand{\arraystretch}{1.5}
\begin{tabular}{@{} >{\bfseries}l @{\hspace{6ex}} >{\raggedright\arraybackslash}p{14cm}}
Software Development & Python, Django, JavaScript, React.js, TypeScript, Node.js, Flutter, Go\\

Technology Ecosystems & Django REST Framework(DRF), FastAPI, RESTful API, Google Cloud Platform(GCP), RDBMS(Postgres, MySQL), NoSQL(MongoDB)\\

QA \& DevOps & Selenium, Docker, Terraform, CircleCI\\

Dev Tools & Git, GitHub, Jupyter Notebook, VS Code, JetBrains, JIRA, Confluence, Slack, Microsoft Teams, Windows, Debian, Ubuntu\\

Core Skills & Clean Code, Troubleshooting, Performance Optimization, Responsive Design, Cross-Browser Compatibility, Unit Testing, Team Collaboration, Agile Methodologies.\\
\end{tabular}\\
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK HISTORY
%----------------------------------------------------------------------------------------

\begin{rSection}{WORK HISTORY}

\textbf{Software Engineer} \hfill Jan 2022 - Apr 2024\\
imranslab \hfill \textit{Montréal, QC (Remote)}
 \begin{itemize}
    \item Developed and maintained web applications using Django and React, ensuring high performance and responsiveness by 30\%.
    \item Collaborated with cross-functional teams to define, design, and ship new features.
    \item Wrote clean, maintainable, and efficient code, enhancing the scalability of inventory management systems by 40\%.
    \item Reduced operational costs by 20\% and improved deployment cycles by 30\% by transitioning legacy systems to a cloud-based infrastructure.
    \item Participated in code reviews and provided constructive feedback to team members.
 \end{itemize}

\textbf{SWE Intern} \hfill Jun 2021 - Dec 2021\\
imranslab \hfill \textit{Montréal, QC (Remote)}
 \begin{itemize}
    \item Refactored 5000 lines of legacy Python code into a modular, maintainable structure adhering to SOLID principles, resulting in a 50\% improvement in code maintainability and a 30\% increase in development speed.
    \item Enhanced troubleshooting efficiency by 25\% by developing and implementing generative AI prompts for debugging. and reducing error resolution time by 40\%.
    \item Led the migration from local servers to cloud infrastructure, improving system scalability and reducing server downtime by 35\%, which enhanced overall system reliability by 45\%.
 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}

\begin{itemize}
    \item \textbf{AI-Enhanced Job Finder:} Developed a job finder platform using Django and React, integrating AI algorithms to refine resume evaluations, boosting match accuracy by 25\%.
    \item \textbf{Trading Analysis Platform:} Re-architected a trading platform using Django and React, achieving a 35\% increase in processing efficiency and a 20\% reduction in latency.
    \item \textbf{Inventory Management System:} Designed and implemented a scalable inventory system using Django, improving data accuracy by 50\% and reducing inventory costs by 15\%.
\end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{EDUCATION}

{\bf B.Sc.(Engg.) in Computer Science and Engineering (CSE)}, Asian University of Bangladesh \hfill {2018 - 2022}

\end{rSection}

%----------------------------------------------------------------------------------------
% DISTINCTIONS
%----------------------------------------------------------------------------------------

\begin{rSection}{DISTINCTIVE MILESTONES \& PASSIONS}

\begin{itemize}
    \item \textbf{Achievements:} Participated in ICPC Regional 2019, Google Kick Start 2021; excelled in national coding contests.
    \item \textbf{Interests:} Passionate about emerging technologies, AI advancements, mentorship, and cinematic arts.
\end{itemize}

\end{rSection}

\end{document}
