\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.4in,top=0.3in,right=0.4in,bottom=0.3in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Jaman Uddin} % Your name
\address{\textbf{Software Engineer}}    % Role you are applying for
\address{+880 167 385-0025 \\ Uttara, Dhaka, Bangladesh}
\address{\href{mailto:swe.jaman.me@gmail.com}{swe.jaman.me@gmail.com} \\ \href{https://github.com/RootProgrammer}{github.com/RootProgrammer}}

% \address{\href{mailto:swe.jaman.me@gmail.com}{swe.jaman.me@gmail.com} \\ \href{https://www.linkedin.com/in/swe-jaman-me/}{linkedin.com/in/swe-jaman-me} \\ \href{https://github.com/RootProgrammer}{github.com/RootProgrammer}}

\begin{document}

%----------------------------------------------------------------------------------------
%	PROFESSIONAL SUMMARY
%----------------------------------------------------------------------------------------

\begin{rSection}{PROFESSIONAL SUMMARY}

{Proactive and results-driven Software Engineer with 2+ years of experience in Python and Django development. Adept at designing scalable software solutions, optimizing system efficiency, and collaborating across teams to deliver impactful projects. Passionate about continuous learning and staying updated on emerging technologies. Skilled in delivering high-quality software aligned with both local and international client needs.}

\end{rSection}

%----------------------------------------------------------------------------------------
% SKILLS
%----------------------------------------------------------------------------------------
\begin{rSection}{KEY SKILLS}

\renewcommand{\arraystretch}{1.5}
\begin{tabular}{@{} >{\bfseries}l @{\hspace{6ex}} >{\raggedright\arraybackslash}p{14.2613cm}}

Programming Languages & Python, Django, JavaScript, TypeScript, React.js, Node.js, Go\\

Frameworks & Django REST Framework, FastAPI\\

Databases & PostgreSQL, MySQL, MongoDB\\

DevOps \& Cloud & Docker, Terraform, Google Cloud Platform\\

Soft Skills & Team Collaboration, Problem Solving, Effective Communication (English)\\

Other Tools & Git, GitHub, JIRA, Confluence, VS Code, Jupyter Notebook\\
\end{tabular}\\
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{WORK EXPERIENCE}

\textbf{Software Engineer} \hfill Jan 2022 - Apr 2024\\
imranslab \hfill \textit{Montréal, QC (Remote)}

\textbf{Development \& Architecture:}
 \begin{itemize}
    \item Designed and implemented scalable Python applications, improving system efficiency by 40\%.
    \item Migrated legacy systems to cloud-based infrastructure, reducing operational costs by 20\%.
    \item Conducted code reviews, ensuring adherence to best practices and industry standards.
 \end{itemize}

\textbf{Project Collaboration:}
 \begin{itemize}
    \item Collaborated with cross-functional teams to translate client requirements into robust solutions.
    \item Worked closely with project managers to meet deadlines and deliver key milestones.
 \end{itemize}

\textbf{Innovation:}
 \begin{itemize}
    \item Integrated modern technologies to streamline workflows and drive continuous improvement.
    \item Conducted technical presentations to share knowledge and foster a culture of innovation.
 \end{itemize}

\textbf{Software Engineering Intern} \hfill Jun 2021 - Dec 2021\\
imranslab \hfill \textit{Montréal, QC (Remote)}

\begin{itemize}
    \item Refactored 5000+ lines of legacy code into modular structures, enhancing maintainability by 50\%.
    \item Spearheaded the migration of local servers to the cloud, reducing server downtime by 35\%.
    \item Worked closely with project managers to meet deadlines and deliver key milestones.
\end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}

\textbf{AI-Enhanced Job Finder:}
 \begin{itemize}
    \item Developed a Django-based job platform integrating AI algorithms for resume evaluation, improving match accuracy by 25\%.
    \item Implemented a recommendation system using machine learning to suggest relevant job listings to users.
 \end{itemize}

\textbf{Inventory Management System:}
 \begin{itemize}
    \item Designed a scalable inventory solution using Django, reducing inventory costs by 15\% and improving data accuracy by 50\%.
 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{EDUCATION}

{\bf B.Sc.(Engg.) in Computer Science and Engineering (CSE)}, Asian University of Bangladesh \hfill {2018 - 2022}

\end{rSection}

%----------------------------------------------------------------------------------------
%	RECOGNITION & COMPETITIONS
%----------------------------------------------------------------------------------------

\begin{rSection}{RECOGNITION \& COMPETITIONS}

\begin{itemize}
    \item Participated in coding contests (ICPC 2018, UVa Online Judge, HackerRank, Google Kick Start 2021) showcasing algorithmic problem-solving skills.
    \item Recognized for outstanding contributions to team-based software development projects.
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	ADDITIONAL DETAILS
%----------------------------------------------------------------------------------------

\begin{rSection}{RADDITIONAL DETAILS}

\begin{itemize}
    \item \textbf{Availability:} Immediate
    \item \textbf{Interests:} Exploring cutting-edge technologies, competitive programming, AI/ML integration
\end{itemize}

\end{rSection}

\end{document}
